%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A template for Wiley article submissions.
% Developed by Overleaf. 
%
% Please note that whilst this template provides a 
% preview of the typeset manuscript for submission, it 
% will not necessarily be the final publication layout.
%
% Usage notes:
% The "blind" option will make anonymous all author, affiliation, correspondence and funding information.
% Use "num-refs" option for numerical citation and references style.
% Use "alpha-refs" option for author-year citation and references style.

\input{designs/default/import.tex}
% \documentclass[blind,alpha-refs]{wiley-article}

% Add additional packages here if required
\usepackage{siunitx}
\usepackage{acronym}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{float}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}

\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 1, % to 2 places
}

% Update article type if known
\papertype{Original Article}
% Include section in journal if known, otherwise delete
\paperfield{Journal Section}

\title{A digital-based1 design methodology for the optimization of high-performance multi-material structures}

% List abbreviations here, if any. Please note that it is preferred that abbreviations be defined at the first instance they appear in the text, rather than creating an abbreviations list.
\abbrevs{}

% Include full author names and degrees, when required by the journal.
% Use the \authfn to add symbols for additional footnotes and present addresses, if any. Usually start with 1 for notes about author contributions; then continuing with 2 etc if any author has a different present address.
\author[1]{W. Zschiebsch}%\authfn{1}
\author[2]{A. Filippatos}
\author[1]{R. Böhm}

%\contrib[\authfn{1}]{Equally contributing authors.}
% Include full affiliation details for all authors
\affil[1]{Leipzig University of Applied Sciences, Faculty of Engineering, Germany}
\affil[2]{Dresden Center for Intelligent Materials, Germany}
\corraddress{Willi Zschiebsch, Leipzig University of Applied Sciences, Faculty of Engineering, Germany}
\corremail{willi.zschiebsch@gmail.com}%????????????????
%\fundinginfo{Funder One, Funder One Department, Grant/Award Number: 123456, 123457 and 123458; Funder Two, Funder Two Department, Grant/Award Number: 123459}%DELETE ????????????????
% Include the name of the author that should appear in the running header
\runningauthor{Zschiebsch et al.}%????????????????

\begin{document}

\acrodef{fdm}[FDM]{finite difference method}
\acrodef{fe}[FE]{finite element}
\acrodef{fea}[FEA]{finite element analysis}
\acrodef{fem}[FEM]{finite element method}
\acrodef{nsa}[NSA]{normal stress averaging}
\acrodef{pia}[PIA]{principle of independent action}

\begin{frontmatter}
\maketitle

\begin{abstract}
A central process in composite lightweight engineering is the design of different fibre-reinforced parts. Some sub-processes such as the construction and numerical failure analysis as well as certain parts of the design process itself can be significantly improved using modern software tools. This often means that a compromise between optimization and increasing development costs must be found in order to balance structural complexity, number of design iteration loops and subsequent changes in the requirements.
We introduce a computer-driven automation process for a multi-domain, parameter-driven design optimization. The proposed concept was built around the idea that the methodology can be used with different software tools that are already in operation in the design process of lightweight structures and therefore allows an easy implementation in already existing development chains.
The developed process was successfully applied to different design scenarios, for example for designing GFRP rotors with respect to their structural dynamics performance. The results show promising time savings during the design phase and allow to quickly adapt the design to subsequent changes in the optimization goal.
\keywords{Composites, Optimization, Design and Modelling, Smart by Design, Design Automation}
\end{abstract}
\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{src/introduction.tex}
\input{src/method.tex}
\input{src/result.tex}
\input{src/discussion.tex}
\input{src/conclusion.tex}
\input{opt/los.tex}

%\section*{acknowledgements}
%Acknowledgements should include contributions from anyone who does not meet the criteria for authorship (for example, to recognize contributions from people who provided technical help, collation of data, writing assistance, acquisition of funding, or a department chairperson who provided general support), as well as any funding or other support information.
%\printendnotes%???????????????????????????
% Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.
\bibliography{sources}
%\include{appendix}
\end{document}
